02_DESeq2

### 2020-02-19 analysis/02_DESeq2.Rmd
now with prl degs

>>>>

head(sexPRLdesg)

PRLhi <- sexPRLdesg %>%
  filter(direction.y == "hi")
PRLhi

PRLwgcna <- read_csv("../results/08_PRL_associated.csv") %>%
  dplyr::rename("gene" =  "x") %>%
  mutate(wgcna = "yes")
PRLwgcna

PRLwgcnaDEGs <- left_join(PRLwgcna, sexPRLdesg) %>%
  select(-direction.x) %>%
  dplyr::rename("PRL" =  "direction.y") 
PRLwgcnaDEGs %>%
  group_by(wgcna, PRL) %>%
  summarize(n = n())
head(PRLwgcnaDEGs)
# 90 of the 98 genes in the wgcna module are also DEGs, with increase expression in hi PRL
```
